Exploiting the Social Graph: Increasing Engagement via Collaborative Interactive Evolution

### 2017-01-27 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Comment about 'via' in the title
@JJ if you have a chance please have a look
Spell check

\begin{abstract}
Interactive evolution, where users' preferences guide the search, is
one of the leading techniques employed by Evolutionary Art
researchers. It is normally implemented as a web application to lower
the access threshold since it often depends on volunteers who visit
the system for fitness assignement. However,  several drawbacks limit
user participation: human fatigue and boredom result from evaluating 
a large number of phenotypes. To tackle these issues, in this paper we
propose an IEC system designed using a human-centered approach, with a
framework consisting of a social network of  
volunteers interacting with a population consisting also of a network 
of phenotypes, which also uses a graph model as a practical 
and efficient tool for mapping the relationships between actors and
objects in the system. A case study is presented as proof-of-concept, 
providing both conceptual and implementation details of a graph based model 
as it is  applied in the implementation of an IEC system. Our
experiments show that the data model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and thus increase {\em performance} of the
interactive system.
\end{abstract}

@@

In this work we propose giving the same
importance to users and their interactions as the population of 
phenotypes have in a traditional EA, even to the extent of using this
knowledge as an integral part of the evolutionary algorithm.
Instead of letting the user assign fitness directly via a rating
or selection system, fitness assignment could depend on the actions of
a group of users, possibly connected in a social network, and depend on how 
they tag, share, rate, or even delete the phenotype. The selection of parents could
also depend on the previous actions, leveraging information such as the fac that  they have the same tag, or shared by
similar users, or whether a leader of opinion liked both or if they are stored in the same collection.
That knowledge could also be applied in choosing which phenotypes whould be presented to a
user, in order to give them those they will find more interesting or useful.

@@

Besides, the methodology presented in this paper for interactive
evolutionary computation is a proposal to frame it as human centered computing \cite{sebe2010human},
in which the context, environment, interfaces, preferences, accesibility, human relations, cognitive
limitations, culture, creativity and other human aspects are an integral part of the system. 
This view requires a multidisciplinary approach, as well as multiple
knowledge representation formalisms. 
As a first step forward, the traditional data model is extended with a graph, in order to have 
yet another view to exploit. In the following section a description of
the data model is presented.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/users_known_1.png}
    \caption{Comparasion of two users showing the {\tt knows} relationship.}
    \label{fig:users-graph}
\end{figure}

@@

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users rating the system. These initial
experiments hint at a possible power law, which might indicate that
the IEC system could be self-organizing, a process that would allow it
to reach a critical state, as has been found in software repositories,
for instance \cite{Merelo2016:repomining}. The dynamics of this kind
of system are fundamentally different, and our future research will
include exploring these aspects of the system. Another line of work would be to study the negative effects of using 
gamification techniques to improve engagement, like cheating or competition.
Finally, the refinement of the proposed Human-Centered frameworkwill need
more case studies and further multi-disciplinary research.

>>>>

\begin{abstract}
Interactive evolution, where users' preferences guide the search, is
one of the leading techniques employed by Evolutionary Art
researchers. It is normally implemented as a web application to lower
the access threshold since it often depends on volunteers who visit
the system for fitness assignment. However,  several drawbacks limit
user participation: human fatigue and boredom result from evaluating 
a large number of phenotypes. To tackle these issues, in this paper we
propose an IEC system designed using a human-centered approach, with a
framework consisting of a social network of  
volunteers interacting with a population consisting also of a network 
of phenotypes, which also uses a graph model as a practical 
and efficient tool for mapping the relationships between actors and
objects in the system. A case study is presented as proof-of-concept, 
providing both conceptual and implementation details of a graph based model 
as it is  applied in the implementation of an IEC system. Our
experiments show that the data model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and thus increase {\em performance} of the
interactive system.
\end{abstract}

@@

In this work we propose giving the same
importance to users and their interactions as the population of 
phenotypes have in a traditional EA, even to the extent of using this
knowledge as an integral part of the evolutionary algorithm.
Instead of letting the user assign fitness directly via a rating
or selection system, fitness assignment could depend on the actions of
a group of users, possibly connected in a social network, and depend on how 
they tag, share, rate, or even delete the phenotype. The selection of parents could
also depend on the previous actions, leveraging information such as the fact that  they have the same tag, or shared by
similar users, or whether a leader of opinion liked both or if they are stored in the same collection.
That knowledge could also be applied in choosing which phenotypes would be presented to a
user, in order to give them those they will find more interesting or useful.

@@

Besides, the methodology presented in this paper for interactive
evolutionary computation is a proposal to frame it as human centered computing \cite{sebe2010human},
in which the context, environment, interfaces, preferences, accessibility, human relations, cognitive
limitations, culture, creativity and other human aspects are an integral part of the system. 
This view requires a multidisciplinary approach, as well as multiple
knowledge representation formalisms. 
As a first step forward, the traditional data model is extended with a graph, in order to have 
yet another view to exploit. In the following section a description of
the data model is presented.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/users_known_1.png}
    \caption{Comparison of two users showing the {\tt knows} relationship.}
    \label{fig:users-graph}
\end{figure}

@@

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users rating the system. These initial
experiments hint at a possible power law, which might indicate that
the IEC system could be self-organizing, a process that would allow it
to reach a critical state, as has been found in software repositories,
for instance \cite{Merelo2016:repomining}. The dynamics of this kind
of system are fundamentally different, and our future research will
include exploring these aspects of the system. Another line of work would be to study the negative effects of using 
gamification techniques to improve engagement, like cheating or competition.
Finally, the refinement of the proposed Human-Centered framework will need
more case studies and further multi-disciplinary research.
